Democratizing Secure Two-Party Computation

### 2017-10-22 OaklandSubmission/ld.tex
nits

\subsubsection*{Correctness theorem} We first define a judgment for
translation of type environments, $\Gamma \vdash \rho \leadsto
\widetilde{\rho}; \widehat{\rho_{1}}, \widehat{\rho_{2}}$. The
judgment is defined inductively on $\Gamma$, and establishes that the
the static environment $\Gamma$ is consistent with the runtime
environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho_{1}}$ and
$\widehat{\rho_{2}}$. As an example, if $x:\kw{uint}^{\mathcal{P}} \in
\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
n$. We elide the judgment, but it is defined in the supplementary
material.

@@

  then $\exists \rho', O_{1}, \widetilde{\rho'}, \chi, \widehat{\rho_{1}'}, \widehat{\rho_{1}'}, O_{2}$, s.t.

  \begin{enumerate}
  \item $\rho \vdash s \Downarrow \rho'; O_{1}$
  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho'}; \chi$
  \item $\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \chi \Downarrow \widehat{\rho_{1}'}, \widehat{\rho_{2}'}; O_{2}$
  \item $\Gamma' \vdash \rho' \leadsto \widetilde{\rho'}; \widehat{\rho_{1}'}, \widehat{\rho_{2}'}$
  \item $O_{1} = O_{2}$
  \end{enumerate}

>>>>

\subsubsection*{Correctness theorem} We first define a judgment for
translation of environments, $\Gamma \vdash \rho \leadsto
\widetilde{\rho}; \widehat{\rho_{1}}, \widehat{\rho_{2}}$. The
judgment is defined inductively on $\Gamma$, and establishes that
the static environment $\Gamma$ is consistent with the runtime
environments $\rho$, $\widetilde{\rho}$, and $\widehat{\rho_{1}}$ and
$\widehat{\rho_{2}}$. As an example, if $x:\kw{uint}^{\mathcal{P}} \in
\Gamma$, the judgment checks that $\rho(x) = \widetilde{\rho}(x) =
n$, for some $n$. We elide the judgment, but it is defined in the
supplementary material.

@@

  then $\exists \rho', O_{1}, \widetilde{\rho}', \chi, \widehat{\rho_{1}}', \widehat{\rho_{1}}', O_{2}$, s.t.

  \begin{enumerate}
  \item $\rho \vdash s \Downarrow \rho'; O_{1}$
  \item $\widetilde{\rho} \vdash \widetilde{s} \Downarrow \widetilde{\rho}'; \chi$
  \item $\widehat{\rho_{1}}, \widehat{\rho_{2}} \vdash \chi \Downarrow \widehat{\rho_{1}}', \widehat{\rho_{2}}'; O_{2}$
  \item $\Gamma' \vdash \rho' \leadsto \widetilde{\rho}'; \widehat{\rho_{1}}', \widehat{\rho_{2}}'$
  \item $O_{1} = O_{2}$
  \end{enumerate}
